---
title: "droughtindex_timelapse2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rayshader)
library(ncdf4)
library(av)
library(lubridate)
library(magick)
library(here)
source("functions.R")

# create the timelapse_images subdirectory if it does not exist
# this is where the image files and video files will be written to
if(!dir.exists(paste0(here::here(), "/timelapse_images"))) {
  dir.create(paste0(here::here(), "/timelapse_images"))
}

```


place all the .nc files in the directory where this file is
assumes they are named by date (as provided e.g. "20200323_NZDI.nc"), as the function will use the date from the file name and use it in the snapshot
```{r}
# lists all the .nc files in this directory and turns this into a tibble
nc_files <- list.files(pattern = ".nc$") %>% 
  enframe(name = NULL, value = "file") %>% 
  mutate(plot_title = lubridate::ymd(stringr::str_extract(file, "[^_]+")))
```

row by row, pass each file listed into the `create_snapshots()` function
```{r}
nc_files <- nc_files %>% 
  mutate(snapshottaken = FALSE,
         snapshottaken = purrr::map2(file, plot_title, create_snapshots))# %>% 
  # unnest(cols = c(snapshottaken))
```

print out the list of dates that did not succesfully generate
```{r}
nc_files %>% 
  filter(snapshottaken == TRUE)
```


create the video file after filtering out the dates that did not successfully generate
```{r}
png_files <- nc_files %>% 
  filter(snapshottaken == TRUE) %>% 
  mutate(png_files = paste0("timelapse_images/", plot_title, ".png")) %>% 
  select(png_files) %>% 
  pull()
png_files <- c(png_files, png_files[length(png_files)])

av::av_encode_video(png_files, 'timelapse_images/nzdi_output.mp4', framerate = 1)
```


